Title Goes Here

### 2020-03-27 analysis/paper/paper.Rmd
tried PCA

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)

@@

@@

plot(CV_ML, CV_BL)
```

>>>>

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)
#list of all attributes without ID
DF <- df[,1:7]

@@

#simpler way to calculate Correlataion, you can use
cor(DF)

#a scatterplot matrix of Correlation
pairs(DF)

@@

#simpler way to calculate CV
sd(ML)/mean(ML)

#PCA 
library(ggbiplot)
PCA <- prcomp(DF, center = TRUE,scale. = TRUE)

ggbiplot(PCA, obs.scale = 1, var.scale = 1,          ellipse = TRUE, circle = TRUE)+
scale_color_discrete (name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')

###I need to figure out how to group them
